\documentclass{resume} % Use the custom resume.cls style
\usepackage{xcolor}
\definecolor{linkgray}{RGB}{70,70,70}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Áron D. Kohlhéb} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+36 30 2651 765 \\ Delft, Netherlands} 
\address{\href{mailto:Kohlheb-1@student.tudelft.nl}{aron.kohlheb@gmail.com} \\ \href{https://nl.linkedin.com/in/aron-domotor-kohlheb-aerospace}{linkedin}}  %
\definecolor{darkblue}{RGB}{0,0,90} % very dark blue
% \href{www.faangpath.com}{www.faangpath.com}} 
\begin{document}

\hypersetup{
    colorlinks=true,
    allcolors=darkblue
}


\begin{rSection}{Education}

{\bf MSc Systems and Control} @ \textit{Delft Center for Systems and Control, TU Delft} \hfill {Sep. 2023 -- Aug. 2026}\\
\textbf{\textit{Coursework:}}  Numerical Linear Algebra, Noise Filtering, System Identification, Distributed Optimization, Hybrid Systems, Sensor Fusion, Model Predictive Control, Dynamic Programming, Stochastic Systems, Tensor Networks, Reinforcement Learning, Deep Learning.\vspace*{1mm}

{\bf BSc Aerospace Engineering} @ \textit{Faculty of Aerospace Engineering, TU Delft} \hfill {Sep. 2019 -- Jun. 2023}\\
Multidisciplinary Systems engineering with basic understanding in mechanical, electrical engineering, aerodynamics, flight dynamics, fundamental engineering tools such as Python, Github, modeling, breaking down complex problems. Minor in AI with project on Convolutional Neural Networks: \href{https://github.com/POTN1K/CompressionFlowAE}{git}. 


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Skills & Python, C++, SQL, MATLAB/Simulink, PLC programming
\\
Control Skills & Kalman Filtering, Sensor Fusion, MPC, Distributed Control, Reinforcement Learning\\
%mention what is required by the application:
Soft Skills & Team work, Communication, Time management  \\
\end{tabular}
\end{rSection}
\begin{rSection}{Experience}

\textbf{Teaching Assistant} @ {Aerospace System Design}\hfill Sep 2023 -- Jan 2026\\
\textit{reference:} \href{https://www.tudelft.nl/staff/s.j.watson/}{Prof. Dr. SJ (Simon) Watson} \hfill \href{https://www.tudelft.nl/en/ae}{Faculty of Aerospace Engineering, TU Delft} \textit{Delft, Netherlands}\\
Each year I taught two groups of ten students on breaking down problems, working consistently, reporting, and coding. 

%\textbf{Annotation Engineer} @ \href{https://www.mapiq.com/}{Mapiq}   \hfill Feb 2023 -- Aug 2023

\textbf{Website Developer} @ \href{https://www.aanmelder.nl/172417}{CURE Project}  \hfill Feb 2022 -- Mar 2023\\
\textit{reference:} \href{https://www.tudelft.nl/en/staff/t.j.heimovaara/}{Prof.dr.ir. TJ (Timo) Heimovaara} \hfill \textit{\href{https://www.tudelft.nl/citg/over-faculteit/afdelingen/geoscience-engineering}{Geoscience \& Engineering, TU Delft}, Delft, Netherlands}\\
Built the data structure (SQL + Python) and from scratch the visual web-interface, both back- and frontend (Nginx \& Gunicorn, Django \& Dash), on a Linux server for data collected by 5 companies and used in research by 3 universities.  


% \textbf{Device Technician}  \hfill Sep 2021 -- Dec 2021\\
% \href{https://flexous.com/}{Flexous} \hfill \textit{\href{https://yesdelft.com/}{YES!Delft}, Delft, Netherlands}


\textbf{Systems Engineer}  @ \href{https://www.teamtumbleweed.eu/mars/}{Team Tumbleweed} \hfill Apr 2021 -- Aug 2022\\
\textit{reference: }\href{https://www.linkedin.com/in/lucascohen-ae/}{Lucas Cohen} \hfill \textit{\href{https://aerospaceinnovationhub.nl/}{Aerospace Innovation Hub}, Delft, Netherlands}\\
Worked on conceptual design, feasibility, and requirements of a Mars rover, our work was positively reviewed by ESA. 


% \textbf{Maths and Physics Tutor} \hfill Sep 2020 -- Jun 2021\\
% For International Baccalaureate A-level exams\hfill \textit{Self-employed, online environment}


\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}


\textbf{\textit{Thesis:}} Building a Reinforcement Learning algorithm to test cyber vulnerabilities of power distribution systems and the learnability of Event-Triggered Control based dynamic lightweight encryption. \vspace*{1mm}\\
\textbf{\textit{Testbed Project:}} Built a real-time hardware-in-the-loop cybersecurity testbed on RTS-PLC-PC setup, developed model and hierarchical control for wind farms: \href{https://github.com/arondomotorkohlheb/off_testbed}{link}. \vspace*{1mm}\\
\textbf{\textit{Tensor Networks for Neural Nets:}} Developed and tested tensor-network compressions and converted backpropagation operators to support the learning of the compressed representation to raise training efficiency: \href{}{link} \vspace*{1mm}.\\
\textbf{\textit{Inverted Pendulum Identification and Control:}} Lagrangian-based modeling aided grey-box system identification, state estimation, LQR and MPC control implementation on a physical system: \href{}{link}.\vspace*{1mm}\\
\textbf{\textit{Distributed \& Networked Control:}} Derived stability bounds on delays in networks and developed distributed LQR under coupling constraints with Lagrangian, consensus, and ADMM methods: \href{}{link}. \vspace*{1mm}\\
\textbf{\textit{Satellite Attitude Control:}} Developed and tested PID and LQR reference tracking controllers for both discrete and continuous model of satellite attitude control: \href{}{link}.
\end{rSection}
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} 

Coach since 2021 and head organizer of trainings for 144 trainees and 18 coaches in 2024--2025 at the beach volleyball club \href{https://www.shotbeach.nl/}{D.S.B.V. Shot}. 


\end{rSection}


\end{document}
í